Model Search in Relational Domains

### 2016-10-21 algorithm.tex
more comment

\paragraph{Solver State.}  \pscmt{This paragraph seems redundant. Doesn't this redefine $\mathcal{T}$?} The state of a ACDCL solver is a tuple 
of the form $\langle \mathcal{E}, S \rangle$.  Here, $\mathcal{E}$ 
is a sequence of labelled information of the form $(m,s)$ where 
$m$ is a meet irreducible and $s = \mathsf{decision}$ if $m$ is a decision, 
or $s = \mathsf{deduction}$ if $m$ is inferred by a deduction. And $S$ is 
a set of abstract deduction transformer \pscmt{???}.  A trail in a SAT solver 
stores variable assignments of the form $(p, t)$, where $p$ is 
a propositional variable that appears at most once in the trail 
and $t$ is a truth assignment (true or false).  Whereas, a trail 
$\mathcal{T}$ in ACDCL contains a sequence of meet irreducibles 
inferred by deduction or decision phase where a variable in trail 
can be assigned \pscmt{constrained?} multiple times, each time with increasingly precise 
bounds \pscmt{that's specific for a particular domain}.  A current valuation $v$ is a meet of all elements of trail
$\mathcal{T}$, such that $v = \top$ when $\mathcal{T}$ is 
empty or $v=\underset{i \geq 0 \wedge i \leq |\mathcal{T}|}{\meet m_i}$, where 
$m_i \in \mathcal{T}$.  A solver is in conflict if some clauses in
$\mathcal{S}$ is not abstractly satisfied by $v$.

%\pscmt{define ``consistent with trail''}

>>>>

\paragraph{Solver State.}  \pscmt{This paragraph seems redundant. Doesn't this redefine $\mathcal{T}$?} The state of a ACDCL solver is a tuple 
of the form $\langle \mathcal{E}, S \rangle$.  Here, $\mathcal{E}$ 
is a sequence of labelled information of the form $(m,s)$ where 
$m$ is a meet irreducible and $s = \mathsf{decision}$ if $m$ is a decision, 
or $s = \mathsf{deduction}$ if $m$ is inferred by a deduction. And $S$ is 
a set of abstract deduction transformer \pscmt{???}.  A trail in a SAT solver 
stores variable assignments of the form $(p, t)$, where $p$ is 
a propositional variable that appears at most once in the trail 
and $t$ is a truth assignment (true or false).  Whereas, a trail 
$\mathcal{T}$ in ACDCL contains a sequence of meet irreducibles 
inferred by deduction or decision phase where a variable in trail 
can be assigned \pscmt{constrained?} multiple times, each time with increasingly precise 
bounds \pscmt{that's specific for a particular domain}.  
\rmcmt{define trail refinement}
\Omit {
A current valuation $v$ is a meet of all elements of trail
$\mathcal{T}$, such that $v = \top$ when $\mathcal{T}$ is 
empty or $v=\underset{i \geq 0 \wedge i \leq |\mathcal{T}|}{\meet m_i}$, where 
$m_i \in \mathcal{T}$.  A solver is in conflict if some clauses in
$\mathcal{S}$ is not abstractly satisfied by $v$.
}
%\pscmt{define ``consistent with trail''}
